04_DESeq_sexes

### 2019-08-27 analysis/04_DESeq2_sexes.Rmd
add lda tutorial

## Starting with all the data

@@

## Run DESeq on all subsets of the data

@@

@@

>>>>

## DEseq2 analysis on characterization. Looking at treatment AND sex for each tissue

@@

@@

## PCA

@@

## Linear discriminant analysis (LDA)

http://www.sthda.com/english/articles/36-classification-methods-essentials/146-discriminant-analysis-essentials-in-r/

```{r LDA}
library(caret)
theme_set(theme_classic())

# Load the data
data("iris")

# Split the data into training (80%) and test set (20%)
set.seed(123)
training.samples <- iris$Species %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data <- iris[training.samples, ]
test.data <- iris[-training.samples, ]

# Normalize the data. Categorical variables are automatically ignored.
# Estimate preprocessing parameters
preproc.param <- train.data %>% 
  preProcess(method = c("center", "scale"))

# Transform the data using the estimated parameters
train.transformed <- preproc.param %>% predict(train.data)
test.transformed <- preproc.param %>% predict(test.data)

# LDA analysis
library(MASS)
# Fit the model
model <- lda(Species~., data = train.transformed)
# Make predictions
predictions <- model %>% predict(test.transformed)
# Model accuracy
mean(predictions$class==test.transformed$Species)

# results
model
plot(model)

# make predictions
predictions <- model %>% predict(test.transformed)
names(predictions)

# Predicted classes
head(predictions$class, 6)
# Predicted probabilities of class memebership.
head(predictions$posterior, 6) 
# Linear discriminants
head(predictions$x, 3)

# LDA plot using ggplot2 
lda.data <- cbind(train.transformed, predict(model)$x)
ggplot(lda.data, aes(LD1, LD2)) +
  geom_point(aes(color = Species))

# model accuracy 
mean(predictions$class==test.transformed$Species)
```
